A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-05 manuscript.Rmd
add a draft of a simple summary

---
title: A Hitchhiker's Guide to Reproducible Research in R
author:
  - name: Aaron Peikert
    affil: 1, *
    orcid: 0000-0001-7813-818X
  - name: Caspar J. Van Lissa
    affil: 2, 3
    orcid: 0000-0002-0808-5024
  - name: Andreas M. Brandmaier
    affil: 1, 4
    orcid: 0000-0001-8765-6982
affiliation:
  - num: 1
    address: |
      Center for Lifespan Psychology---Max Planck Institute for Human Development
      Lentzeallee 94, 14195 Berlin, Germany
  - num: 2
    address: |
      Department of Methodology & Statistics---Utrecht University faculty of Social and Behavioral Sciences, Utrecht, Netherlands
  - num: 3
    address: |
      Open Science Community Utrecht, Utrecht, Netherlands
  - num: 4
    address: |
      Max Planck UCL Centre for Computational Psychiatry and Ageing Research
      Berlin, Germany and London, UK
# firstnote to eighthnote
correspondence: |
  peikert@mpib-berlin.mpg.de
journal: psych
type: tutorial
status: submit
bibliography: temp.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: "`r tryCatch(trimws(readr::read_file(here::here('abstract.Rmd'))))`"
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  The authors declare no conflict of interest.
abbreviations:
  - short: GUI
    long: Graphical User Interface
  - short: CLI
    long: Comand Line Interface
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
    - pander
    - lavaan
    - furrr
    - future.batchtools
    - rticles
    - moments
    - report
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
  data:
    - data/simulation_results.csv
output:
  bookdown::markdown_document2:
    base_format: rticles::mdpi_article
header-includes:
   - \usepackage[labelformat=empty]{caption}
   - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}, numbers=left}
---

>>>>

---
title: A Hitchhiker's Guide to Reproducible Research in R
author:
  - name: Aaron Peikert
    affil: 1, *
    orcid: 0000-0001-7813-818X
  - name: Caspar J. Van Lissa
    affil: 2, 3
    orcid: 0000-0002-0808-5024
  - name: Andreas M. Brandmaier
    affil: 1, 4
    orcid: 0000-0001-8765-6982
affiliation:
  - num: 1
    address: |
      Center for Lifespan Psychology---Max Planck Institute for Human Development
      Lentzeallee 94, 14195 Berlin, Germany
  - num: 2
    address: |
      Department of Methodology & Statistics---Utrecht University faculty of Social and Behavioral Sciences, Utrecht, Netherlands
  - num: 3
    address: |
      Open Science Community Utrecht, Utrecht, Netherlands
  - num: 4
    address: |
      Max Planck UCL Centre for Computational Psychiatry and Ageing Research
      Berlin, Germany and London, UK
# firstnote to eighthnote
correspondence: |
  peikert@mpib-berlin.mpg.de
journal: psych
type: tutorial
status: submit
bibliography: temp.bib
appendix: appendix.tex
simplesummary: |
  People trust science because other experts can vet it.
  For example, suppose another person than the author of an article can recreate the same results on another computer.
  In that case, they can more easily trust that the results are correct.
  If anyone can recreate an article, it is called "reproducible".
  We explain common technical problems (e.g. making sure that: 1. nothing has changed, 2. there are no copy-and-paste errors, 3. all steps are in the correct order, and 4. that the necessary software is installed) of reproducibility and show technical solutions.
  However, because these solutions are complicated to use, we have developed some helpers to make them more accessible.
  We then discuss why reproducibility also helps researchers to be more productive and produce higher-quality research.
  One example is that with reproducibility, researchers can plan studies and their analyses with great precision.
  If they publish such a plan, this is called "preregistration".
  We urge researchers to formulate their data analysis for a preregistration as computer code because computer code is more precise than describing it with words.
  They then should write all other parts of the preregistration with the same standards as a scientific article.
  We call this preregistration as code.
  Such a precise plan is beneficial for science because researchers generally trust results more if they are not explained after the fact.
abstract: "`r tryCatch(trimws(readr::read_file(here::here('abstract.Rmd'))))`"
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  The authors declare no conflict of interest.
abbreviations:
  - short: GUI
    long: Graphical User Interface
  - short: CLI
    long: Comand Line Interface
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
    - pander
    - lavaan
    - furrr
    - future.batchtools
    - rticles
    - moments
    - report
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
  data:
    - data/simulation_results.csv
output:
  bookdown::markdown_document2:
    base_format: rticles::mdpi_article
header-includes:
   - \usepackage[labelformat=empty]{caption}
   - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}, numbers=left}
---
